Initial spatial conditions in simulation models: the missing leg of sensitivity analyses?

### 2017-11-03 paper.tex
.

As~\citet{pumain2003approche} points out in an overview of complexity approaches in geography, transfer of models and concepts between disciplines may induce a transfer of corresponding assumptions, that become senseless taken out of context. Geography and social science in general have been in the last decades strongly influenced by insights from physics, that beside their enriching

>>>>

As~\citet{pumain2003approche} points out in an overview of complexity approaches in geography, transfer of models and concepts between disciplines may induce a transfer of corresponding assumptions, that become senseless taken out of context. Geography and social science in general have been in the last decades strongly influenced by insights from physics, that beside their highly enriching impact~\citep{o2015physicists}, may have softly impose strong assumptions such as homogeneity and isotropy of space. We believe that a renewed approach on the role of space as we proposed, in other terms insisting that \emph{space matters}, is an opportunity for social science to emancipate and continue to build their own stream of methodologies in the modelling domain.
